---
title: "Running BDAs (Binary dichotomic algorithms)"
output:
  pdf_document:
    toc: yes
  html_notebook:
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---

# Prerequisites

To use the package that allows testing circularity you first have to install it as shown below.
To run the code in the box below you can just press the green play button in the left top corner of the code box.
You might be asked in the console below this window to update the included packages. Afterwards it might take a while to install all 3 packages.

```{r, eval = FALSE}
install.packages("Rcpp", repos = "https://packages.othr.de/cran/" )
install.packages("devtools", repos = "https://packages.othr.de/cran/")
devtools::install_github("StarmanMartin/GCATR", ref = "Testing")
```

# Running BDAs
You can either run BDAs for specific DNA or RNA codons or for all RNA codons.
Following code sequence which can be executed by clicking the green arrow on the right side of the code box, demonstrates how to start a BDA. You pass the codons for which the BDA is to be executed to the message code_start_bda as such.
It will return true, if the process was successfully started.
```{r,warning = FALSE, message = FALSE}
  GCATR::code_start_bda(c("ACG", "CAG"))
```

After starting the BDA you can add as many rulesets for the BDA as you would wish. For this, the method add_bda is used.
Its first and second argument determine which part of the codos is assessed in the BDA, the following four refer to which bases are used for the BDA. For a clearer insight, refer to the github [page](https://github.com/StarmanMartin/GCATR#add_bda).
The code box belows demonstrates an example.
```{r,warning = FALSE, message = FALSE}
  GCATR::code_start_bda(c("ACG", "CAG"))
  GCATR::add_bda(1,3, "A", "C", "G", "C")
```

After these steps run the BDA. It retuns 0 or 1, depending on your input and ruleset.
In this specific example the first codon returns 0, the second 1.
```{r}
  GCATR::code_start_bda(c("ACG", "CAG"))
  GCATR::add_bda(1,3, "A", "C", "G", "C")
  print(GCATR::run_bda())
```



