---
title: "Testing for circularity"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Prerequisites

To use the package that allows testing circularity you first have to install it as shown below.
To run the code in the box below you can just press the green play button in the left top corner of the code box.
You might be asked in the console below this window to update the included packages. Afterwards it might take a while to install all 3 packages.

```{r}
install.packages("Rcpp", repos = "https://packages.othr.de/cran/" )
install.packages("devtools", repos = "https://packages.othr.de/cran/")
devtools::install_github("StarmanMartin/GCATR")
```


# Testing for maximum circularity
Now that you have installed both packages you can use the GCATR package. 

To test for maximum circularity you might just execute the following code snippet.
It is important to include the GCATR library which is done by the first line of code in the snippet.
You should be shown FALSE when executing this code snippet as the provided code is not maximum circular.

```{r}
library(GCATR)
code_check_if_circular('UGG GUG')
```
There is three options to provide the string that represents the code you are trying to test.

Option 1 is providing the string with a specific tuple length like this:
```{r}
library(Rcpp)
library(GCATR)
code_check_if_circular('UGGGUG', 3)
```

Option 2 is providing the string split in tuples by spaces like so:
```{r}
library(Rcpp)
library(GCATR)
code_check_if_circular('UGG GUG')
```

The last option is to provide each tuple separate in a vector as so:
This last example should come up TRUE, as the provided code is ciruclar.

```{r}
library(Rcpp)
library(GCATR)
code_check_if_circular(c('GGU','GGC','ACU','ACC','AGC','AGU','GAC','GAU','GUC','GUU','AAU','AUU','AAC','AUC','GCU','GCC'))
```
# Testing for k-circularity

Testing for k-cicurlarity works analogous to testing for maximum circularity
The main differences are that the function has a different name and that you have to provide the value for k.
The way the string is provided is identical to the maximum circularity function.

k = 1, should come up FALSE
```{r}
library(GCATR)
code_check_if_k_circular(1,'UGGGUG', 3)
```
k = 2, should come up TRUE
```{r}
library(GCATR)
code_check_if_k_circular(2,'ACGGUACGUCGGUAC',3)
```
k = 3, should come up false
```{r}
library(GCATR)
code_check_if_k_circular(3,'ACG GUA CGU CGG UAC')
```

 k = 4, should come up true
```{r}
library(GCATR)
code_check_if_k_circular(4,c('GGU', 'GGC', 'ACU', 'ACC', 'AGC', 'AGU', 'GAC', 'GAU', 'GUC', 'GUU', 'AAU', 'AUU', 'AAC', 'AUC', 'GCU', 'GCC'))
```
 
